\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=0.4in, right=0.4in, top=0.3in, bottom=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{wrapfig}

% Define colors
\definecolor{darkblue}{RGB}{0,0,128}

% Set up hyperref
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

% Adjust section and subsection formatting
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titleformat{\subsection}{\bfseries}{\thesubsection}{1em}{}

\begin{document}

\pagestyle{empty}

\begin{center}
    \textbf{\LARGE Petteri Vänttinen} \\
    Address: ADDRESS \\
    Phone: PHONE \\
    Email: EMAIL \\
    LinkedIn: \href{https://www.linkedin.com/in/petteri-vanttinen-a4b388272/}{linkedin.com/in/petteri-vanttinen-a4b388272} \\
    GitHub: \href{https://github.com/PetteriV99}{github.com/PetteriV99}
\end{center}

\section*{Profile}

I am open for new challenges and projects as a recently graduated engineer. I worked on customer projects in theFirma as part of my degree, such as a web application for Gamu RY . I focused on software engineering and I am looking for coding as part of my career. Right now I am improving my skills in Full Stack development and working on Full Stack Open Course. I am ready to relocate and begin work as soon as possible.

\section*{Education}
\subsection*{\textbf{Turku University of Applied Sciences}, Degree Programme in Information and Communication Technology, Sep 2019 -- June 2023}
\begin{itemize}
    \item Competence track in Software Engineering and Project Management. Project work done in \href{https://www.turkuamk.fi/fi/artikkelit/3090/thefirma-tarjoaa-palveluita-asiakkaille-ja-mahdollisuuksia-opiskelijoille/}{theFirma project office}. Thesis on \href{https://www.theseus.fi/handle/10024/803366}{integration of web services}.
    \item PMAF Project Management Foundation Certificate (IPMA D)
\end{itemize}

\section*{Skills}
\begin{itemize}
    \item JavaScript, Python, Web Development, React / React Native, Node.js, MongoDB, Postgres, Docker, Git, Figma
\end{itemize}

\section*{Projects}
\subsection*{Full Stack Open Parts 0-5, Full Stack Web Development, Jul 2023 -- Aug 2023}
\begin{itemize}
    \item Completed the core part of the \href{https://fullstackopen.com/en/part0/general_info}{course}.
    \item Technologies used: React, Node, Express, Jest, Cypress.
\end{itemize}

\subsection*{Diginavi 2.0, May 2023 -- Jun 2023}
\begin{itemize}
    \item Developed as full-stack, web application project for theFirma. Worked on implementing recovery and feedback processes for REST API and React frontend. Used Figma to design new pages.
    \item Build a web server for deployment using Linux, Docker and nginx. Made a Gitlab devops pipeline for automatically testing and building of Docker images. 
\end{itemize}

\subsection*{EntreFox Mobile Application, Sep 2022 -- Dec 2022}
\begin{itemize}
    \item Developed for theFirma using React Native. Worked on finding and fixing issues. Lead a small team of new students and gave small lessons on the used technologies and application development.
\end{itemize}

\section*{Experience}
\subsection*{Kushiro National College of Technology, Exchange Studies, May 2022 -- Aug 2022}
\begin{itemize}
    \item Implemented a Python application using tkinter GUI framework. Completed a small research project on typical loading bars in user interfaces. Designed application using Figma.
\end{itemize}
\subsection*{Finserve Oy, Developer Intern, May 2021 -- Jun 2021}
\begin{itemize}
    \item Worked on changing page contents and layouts in Wordpress. Designed a web site using Figma.
\end{itemize}
\subsection*{Tietokonekauppa Oy, Developer Intern, Jul 2020 -- Aug 2020}
\begin{itemize}
    \item Repaired computers and other IT equipment by cleaning, changing components and updating software. Provided help in the main store, collecting and sending packages for the web store.
\end{itemize}

\end{document}
